---
name: Ivan Castro
phone: 315 744 6821
www: iecastro.github.io
email: "iecastro@syr.edu"
github: iecastro
linkedin: iecastro
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 2d2d2d
docname: Resume
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(vitae)
```


# Relevant Skills

## Data Science

* Statistical programming, Data wrangling, Visualization, Modelling, Spatial analysis, Communication

## Applications

* RStudio, ArcGIS, SPSS, MS Access, Qualtrics


# Education
```{r}
tribble(
  ~ uni, ~ degree, ~ loc, ~ dates,
  "MSPH in Biostatistics", "Syracuse University", "Syracuse, NY", "Aug. 2016 - May 2018",
  "BA in  Psychology", "SUNY Oswego", "Oswego, NY", "Aug. 2010 - Dec. 2013") %>% 
  detailed_entries(degree, dates, uni, loc)

```


# Relevant Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Research Coordinator", "VISN 2 Center for Integrated Healthcare", "Syracuse, NY", "Aug. 2018 - Present", "Administration and management of NIH R34 (treatment development) grant",
  "Project Manager", "Syracuse University", "Syracuse, NY", "Apr. 2015 - May 2019", "Administration and management of NSF training grant",
  "Research Assistant", "Syracuse University", "Syracuse, NY", "May 2016 - May 2018", "",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```


# Publications

__Castro, I. E.__, Larsen, D. A., Hruska, B., Parson, P. J., Palmer, C. D., and Gump, B. B. (2019). Variability in the spatial density of vacant properties contributes to background lead (Pb) exposure in children. Environmental Research, 170, 463-471.

# Presentations

Dykas, M. J., __Castro, I. E.__, Wolford, K., & Gump, B. B. (April 2018). Psychological flexibility moderates the link between combat exposure and hopelessness in military veterans. ResilienceCon, Nashville, TN.

__Castro, I. E.__ and Dykas, M. J. (March 2018).  Close Relationships among service-members moderate the link between combat and PTSD symptomatology. Poster accepted to Eastern Psychological Association Annual Meeting. Philadelphia, PA. 

__Castro, I. E.__ and Dykas, M. J. (March 2016). The implications of social support and resilience in a Veteran's wellbeing.  Symposium presented at Eastern Psychological Association Annual Meeting. New York, NY.


