---
name: Ivan Castro
www: iecastro.netlify.com
email: "iecastro@syr.edu"
github: iecastro
linkedin: iecastro
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 2d2d2d
docname: Resume
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(vitae)
```

# Relevant Skills

## Data Science

* Statistical programming, Data wrangling, Visualization, Modelling, Spatial analysis, Communication

## Applications

* RStudio, ArcGIS, SPSS, MS Access, Qualtrics

# Education
```{r}
tribble(
  ~ uni, ~ degree, ~ loc, ~ dates,
  "MSPH in Biostatistics", "Syracuse University", "Syracuse, NY", "Aug 2016 - May 2018",
  "BA in  Psychology", "SUNY Oswego", "Oswego, NY", "Aug 2010 - Dec 2013") %>% 
  detailed_entries(degree, dates, uni, loc)

```

# Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data Analyst", "innoVet Health", "Syracuse, NY", "Jan 2020 - present", "",
  "Research Coordinator", "VISN 2 Center for Integrated Healthcare", "Syracuse, NY", "Aug 2018 - Jan 2020", "Management of NIH R34 (treatment development) grant",
  "Research Coordinator", "VISN 2 Center for Integrated Healthcare", "Syracuse, NY", "Aug 2018 - Jan 2020", "Coordination of behavioral clinical trial",
  "Project Manager", "Syracuse University", "Syracuse, NY", "Apr 2015 - May 2019", "Management of NSF-funded training grant",
  "Research Assistant", "Syracuse University", "Syracuse, NY", "May 2016 - May 2018", "Graduate RA in the Department of Public Health") %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Publications

**Castro, I. E.**, Hruska, B., and Gump, B. B. (2020). *Race differences in the effect of Subjective Social Status on hostility and depressive symptoms among 9- to 11-year-old Children* J. Racial and Ethnic Health Disparities. *In Press.*  

__Castro, I. E.__, Larsen, D. A., Hruska, B., Parson, P. J., Palmer, C. D., and Gump, B. B. (2019). *Variability in the spatial density of vacant properties contributes to background lead (Pb) exposure in children.* Environmental Research, 170, 463-471.

# Presentations

**Castro, I. E.**, Crinnin, C., Mastroleo, N., King, P., Balderrama-Durbin, C., Rauch, S., & Possemato, K. (November 2019). *A Delphi study to integrate Prolonged Exposure for Primary Care and Motivational Enhancement Therapy for heavy alcohol use.* International Society for Traumatic Stress Studies Annual Meeting. Boston, MA.  

Olson, K., Hruska, B., **Castro, I. E.**, Suffoletto, B., Callaway, C., & Pacella-LaBarbara, M. (October 2019). *The impact of neighborhood deprivation on acute psychological and pain-related outcomes following traumatic injury.* Science 2019. University of Pittsburgh, PA.    

Dykas, M. J., __Castro, I. E.__, Wolford, K., & Gump, B. B. (April 2018). *Psychological flexibility moderates the link between combat exposure and hopelessness in military veterans.* ResilienceCon, Nashville, TN.  

__Castro, I. E.__ and Dykas, M. J. (March 2018). *Close Relationships among service-members moderate the link between combat and PTSD symptomatology.* Eastern Psychological Association Annual Meeting. Philadelphia, PA.   

__Castro, I. E.__ and Dykas, M. J. (March 2016). *The implications of social support and resilience in a Veteran's wellbeing.*  Eastern Psychological Association Annual Meeting. New York, NY.  


